### 2019-04-24 reviews/icfp-rebuttal.md

For example, `parallel` has the following type, given in Haskell syntax:
```
parallel
  :: ITask a
  => [ ( ParallelTaskType, ParallelTask a ) ]
  -> [ TaskCont [ ( Int, TaskValue a ) ] ( ParallelTaskType, ParallelTask a ) ]
  -> Task [ ( Int, TaskValue a ) ]
```
Where `ITask` is a type class that provides serialisation, datatype generic representations,
run-time type information, and generation of graphical editors.
The main challenge solved in this work is
trimming this combinator down to two elementary combinators (⋈ and ⧫) which,
together with shared memory (■), can model most of its use cases.
We did not give this example in section 1.4, where it belongs.

Furthermore, we were able to significantly simplify the step combinator using the
insight that the fail task (☇) is a basic task which will never have an observable value
and can be used for guards.

Also, our system simplifies the notion of editors and connects them to the already existing notion of widgets.

All these points are not sufficiently emphasised in the paper.

@@

### Application

It is true that the paper does not use the semantics to prove properties about tasks.
This is intentional.
In this work, we focus on introducing the core concepts of TOP,
linking them to a formal description,
showing that this description is sane,
and putting the resulting language into context by comparing it to other similar systems.
These four things lead to a holistic description of TOP which can be used for further research as well as implementation.

In an upcoming article, we are using our system to symbolically execute tasks.
<!-- Moet zo'n verwijzing er in?  --TS -->
<!-- Ja!  --mkl -->
["Proving task properties using symbolic TopHat", to be submitted to IFL'19.]
Symbolic execution allows us to prove properties like "breakfast will always be served" (ex 3.1),
"passengers always get a seat", and "no two passengers can book the same seat" (ex 2.1).
It will be possible to relate traces of inputs to tasks and observations on them,
a suggestion made by reviewer A.

@@

Our grammar only allows putting values of basic types in references.
This is a deliberate choice to exclude recursion by using references.
This means the following are not possible:

* ■l where l : Int -> Int
* ■l where l : Task Int

#### Race conditions and distributed systems

Line 363, which states that our model supports distributed applications,
should not have reached the submitted version.
The system can only "generate _multi-user applications_ to support [...] workflows":
multiple users can interact with an application running on a single server.
It is the users who are distributed, but their events are serialised by the server before being fed to the program.

### 2019-04-24 sections/intuition.tex
shorten code examples

\lstset{emph={makeDrink,makeFood}}

@@

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink. \makeFood. makeDrink <&> makeFood in
  makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? enjoyBreakfast
\end{TASK}

>>>>

\lstset{emph={mkDrink,mkFood}}

@@

\begin{TASK}
  let mkBrkfst : Task Drink -> Task Food -> Task <<Drink,Food>>
    = \mkDrink. \mkFood. mkDrink <&> mkFood in
  mkBrkfst (mkTea <?> mkCoffee) mkEgg >>? enjoyMorning
\end{TASK}

### 2019-04-24 sections/language.tex
convert back to two column layout
rename main tex file to main
shorten code examples

\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\columnwidth,page=3]{figures/drawings-crop.pdf}
  \caption{
    Possible states of an editor and its transitions.
    Shared editors cannot be cleared.
  }
  \label{fig:editor-state}
\end{figure}

@@

We illustrate the use of internal and external choice by means of
an example that asks users to proceed with a given task or to cancel.
If the user does not make a choice within a given time frame, the program proceeds automatically.
The example makes use of the task \TS{wait} from \cref{exm:wait}.
\begin{TASK}
  let cancel : Task Unit = edit <<>> in
  let delay : Int -> Task Unit -> Task Unit = \n : Int. \proceed : Task Unit.
    (proceed <?> cancel) <|> (wait n >>= \u : Unit. proceed)
\end{TASK}
Note that \TS{delay} is higher-order.
It is a task which takes another task as parameter.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth,page=3]{figures/drawings-crop.pdf}
  \caption{
    Possible states of an editor and its transitions.
    Shared editors cannot be cleared.
  }
  \label{fig:editor-state}
\end{figure}

@@

We illustrate the use of internal and external choice by means of
an example that asks users to proceed with a given task or to cancel.
If the user does not make a choice within a given time frame, the program proceeds automatically.
The example makes use of the task \TS{wait} from \cref{exm:wait}.
\begin{TASK}
  let cancel : Task Unit = edit <<>> in
  let delay : Int -> Task Unit -> Task Unit = \n. \proceed.
    (proceed <?> cancel) <|> (wait n >>= \u : Unit. proceed)
\end{TASK}
Note that \TS{delay} is higher-order.
It is a task which takes another task as parameter.
